Information Disclosure in Dynamic Innovation Contests

### 2025-05-27 paper/Paper.tex
update

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.078 & 1.711 & 14.645 & 2.777 & 1.103 & -0.010 \\
 Posterior Stderr   & 0.382 & 0.661 & 3.986 & 0.503 & 0.303 & 2.026 \\
 RMSE                  & 0.401 & 0.694 & 4.002 & 0.925 & 0.320 & 2.026 \\
 95\% Interval        
		& [0.55, 1.99] 
		& [0.77, 3.30]
		& [7.8, 23.0]
		& [1.94, 3.93]
		& [0.61, 1.79] 
		& [-3.97, 4.00] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.215 & 1.647 && 1.969 & 1.079 &\\
Posterior Stderr & 0.120 & 0.178 && 0.143 & 0.130 &\\
RMSE               & 0.121 & 0.231 && 0.146 & 0.152 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 && 1.911 & 1.053 &\\
Posterior Stderr & 0.090 & 0.129 && 0.096 & 0.090 &\\
RMSE                & 0.105 & 0.230 && 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 && 1.981 & 0.990 &\\
Posterior Stderr & 0.059 & 0.090 && 0.069 & 0.059 &\\
RMSE                & 0.060 & 0.165 && 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.840 & 0.835 & . & 1.944 & 1.142 &\\
Posterior Stderr   & 0.138 & 0.152 & . & 0.226 & 0.245 &\\
RMSE                  & 0.276 & 0.174 & . & 0.233 & 0.283 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & . & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.307 & 0.341 & . & 2.187 & 1.034 &\\
Posterior Stderr   & 0.020 & 0.033 & . & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & . & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 31 and 40 times in the 6-month contest, and 143 and 182 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.718 & 3.184 & [-7.064, 5.627] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.259\textbf{**} & 1.089 & [1.089, 5.429] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.109} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.097} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.376, Jarque-Bera = 0.070, Skewness = $-0.041$, Kurtosis = 3.125. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.244.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\centering
	\captionof{figure}{...}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\centering
	\captionof{table}{...}
\end{minipage}
\medskip

>>>>

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Synthetic Data}\label{tbl-contest90}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$} \\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0 \\
\midrule
 Posterior Mean    & 1.078 & 1.727 & 14.588 & 2.759 & 1.090 & 0.062 \\
 Posterior Stderr   & 0.381 & 0.655 & 3.894 & 0.494 & 0.297 & 4.981 \\
 RMSE                  & 0.400 & 0.693 & 3.916 & 0.905 & 0.310 & 4.981 \\
 95\% Interval        
		& [0.54, 2.00] 
		& [0.76, 3.33]
		& [7.8, 22.8]
		& [1.94, 3.86]
		& [0.59, 1.76] 
		& [-9.72, 9.78] \\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 28 and 18 times respectively.
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Pooled Synthetic Data}\label{tbl-pool-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\addlinespace[0.25ex]
\cline{2-7}
\addlinespace[0.25ex]
(true val.)        & 1.2 & 1.5 & 15.0 & 2.0 & 1.0 & 0.0\\
\midrule
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 5 Contests}} \\
Posterior Mean  & 1.112 & 1.508 & 13.774 & 1.974 & 1.081 & 0.239 \\
Posterior Stderr & 0.335 & 0.466 & 3.984 & 0.145 & 0.128 & 5.168 \\
RMSE               & 0.347 & 0.466 & 4.168 & 0.148 & 0.151 & 5.174 \\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 10 Contests}} \\
Posterior Mean  & 1.255 & 1.690 && 1.911 & 1.053 &\\
Posterior Stderr & 0.090 & 0.129 && 0.096 & 0.090 &\\
RMSE                & 0.105 & 0.230 && 0.131 & 0.105 &\\
\addlinespace
\multicolumn{5}{l}{\textbf{Pool of 20 Contests}} \\
Posterior Mean  & 1.206 & 1.639 && 1.981 & 0.990 &\\
Posterior Stderr & 0.059 & 0.090 && 0.069 & 0.059 &\\
RMSE                & 0.060 & 0.165 && 0.071 & 0.060 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
}
\end{minipage}
\end{table}

@@

\begin{table}[htbp]
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\centering
\caption{Bayesian Estimates from Long Term Synthetic Data}\label{tbl-longterm-synthetic-data}
\begin{tabularx}{\textwidth}{lYYYYYY}
\toprule
\textbf{Parameters} & \textbf{$c_i$} & \textbf{$c_j$} & \textbf{$r$} & \textbf{$\sigma$} & \textbf{$\lambda$} & \textbf{$\mu_0$}\\
\midrule
\multicolumn{5}{l}{\textbf{Contest of 6 Months}} \\
True Value           & 0.6     & 0.75   & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.736 & 0.914 & 15.606 & 1.944 & 0.959 & 0.173\\
Posterior Stderr   & 0.177 & 0.240 & 3.358 & 0.205 & 0.152 & 4.948\\
RMSE                  & 0.223 & 0.291 & 3.412 & 0.213 & 0.158 & 4.951\\
\addlinespace
\multicolumn{5}{l}{\textbf{Contest of 12 Months}} \\
True Value           & 0.3     & 0.375 & 15.0 & 2.0     & 1.0     & 0.0\\
Posterior Mean    & 0.259 & 0.383 & 12.692 & 0.949 & 1.034 &\\
Posterior Stderr   & 0.020 & 0.033 & . & 0.127 & 0.098 &\\
RMSE                  & 0.021 & 0.047 & . & 0.226 & 0.102 &\\
\bottomrule
\addlinespace[0.5ex]
\end{tabularx}
\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) $\text{MSE}(\hat\theta) = \mathbb{E}(\hat{\theta}-\theta)^2 = [\mathbb{E}(\hat{\theta}) - \theta]^2 + Var(\hat{\theta})$ by the bias–variance decomposition. RMSE is then calculate by the squared root of MSE. 
(2) Players $i$ and $j$ submit 59 and 51 times in the 6-month contest, and 154 and 90 times in the 12-month contest, respectively.
}
\end{minipage}
\end{table}

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.733 & 3.181 & [-7.073, 5.607] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.264\textbf{**} & 1.088 & [1.096, 5.432] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.110} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.098} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.378, Jarque-Bera = 0.071, Skewness = -0.042, Kurtosis = 3.126. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.244.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\centering
	\captionof{figure}{...}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\centering
	\captionof{table}{...}
\end{minipage}
\medskip
